### 2015-03-09 abstract.tex
minor update to abstract
change name to CRI
updates to abstract

The primary goal of this work is to provide a general framework for what a software development organization
should measure and how to report on those measurements.  The focus is scoring of the entire
organization and not just the development efforts.  The secondary goal of this work is to provide
a software implementation of that framework.

>>>>

The primary goal of this work is to provide a general framework for what a software development organization
should measure and how to report on those measurements.  The focus is providing a single number
to represnet the entire
organization and not just the development efforts.  That single number is considered the CRI score. The secondary goal of this work is to provide
a framework for storing the necessary data.
